Multisensor Architecture for an Intersection Management System

### 2019-01-28 last_version.tex
Format improved in section 3.1 and 3.2.
Figures reordered and format improved in sections 2.3.4
updated changelog
Updated changelog with pages number.

\begin{titlepage}
    \begin{center}
%        \vspace*{1cm}
%        \Huge        
%        Multisensor Architecture for an Intersection Management System
%   
%        \vspace{3.5cm}
%        \LARGE
%        Gustavo Adolfo Velasco-Hernandez
%        
%        \vfill
%        \large
%		        
%        
%        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
%        
%        \vspace{2cm}
%        
%        Advisor: Prof. Eduardo Caicedo Bravo
%		
%		\vspace{2cm}
%        
%        %\includegraphics[width=0.4\textwidth]{university}
%        Perception and Intelligent Systems Research Group \\
%        School of Electrical and Electronics Engineering\\
%        Universidad del Valle\\
%        Colombia\\
%        \today
%\vfill
\todo{Update version message and link}
Version: 1.1 \\
\vspace{2cm}

@@

\subsection*{Revision history}
\subsubsection*{Version 1.1 - 2019-01-24:}

	\begin{itemize}
	\item Updated link for last version downloading
	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
	\item Fixed V2I description in figure 1.6 (1.2.1)
	\item Reworded description of processing stages in section 2.1.1
	\item Described three transportation simulation models (2.2.1)
	\item Added information about contribution in section 4.1 (Articles, events and journals)
	\end{itemize}

>>>>

\begin{titlepage}
    \begin{center}
%        \vspace*{1cm}
%        \Huge        
%        Multisensor Architecture for an Intersection Management System
%   
%        \vspace{3.5cm}
%        \LARGE
%        Gustavo Adolfo Velasco-Hernandez
%        
%        \vfill
%        \large
%		        
%        
%        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
%        
%        \vspace{2cm}
%        
%        Advisor: Prof. Eduardo Caicedo Bravo
%		
%		\vspace{2cm}
%        
%        %\includegraphics[width=0.4\textwidth]{university}
%        Perception and Intelligent Systems Research Group \\
%        School of Electrical and Electronics Engineering\\
%        Universidad del Valle\\
%        Colombia\\
%        \today
%\vfill
%\todo{Update version message and link}
Version: 1.1 \\
\vspace{2cm}

@@

\subsection*{Revision history}
\footnotesize
\subsubsection*{Version 1.1 - 2019-01-28:}

	\begin{itemize}
	\item Updated link for last version downloading
	\item Detailed processing levels in JDL model  in section 1.1.1 (p.15)
	\item Detailed categories in data fusion architectures in section 1.1.2 (p.17)
	\item Fixed V2I description in figure 1.6 (p.21)
	\item Reworded description of processing stages in section 2.1.1 (p.34)
	\item Described simulation models used in transportation (p.35)
	\item Explained design considerations in section 2.3 (p.36)
	\item Figures reordered, format improved and details added in section 2.3.4 (p.39)
	\item Figures merged in sections 3.1 and 3.2 (p.50)
	\item Detailed Test configurations in section 3.2 (p.51)
	\item Figures and tables reordered in section 3.3 (p.52)
	\item Added results summary in table 3.3 (p.54)
	\item Added detailed information about contributions in section 4.1 (p.58)
	\end{itemize}
